Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-08-27 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper
Update expertise_2024_07_19_MK.Rmd

   work_data <-
     read_tsv(file = paste0("data/", i),
              locale = locale(decimal_mark = ",")) %>%
     dplyr::select(Group,
                   Participant,
                   TOI,
                   starts_with("Total_duration_of_fixations"),
                   starts_with("Average_duration_of_fixations"),
                   starts_with("Number_of_fixations"),
                   starts_with("Time_to_first_fixation")
     )

@@

XXX 223 (ist eine Doppelung der 214) --> Daten nochmal komplett neu ziehen!! XXX

@@

# filter group, participants, total duration & number fixation (micro-teaching unit)
df_aoi %>%
  filter(TOI == "Lesson") %>% 
  dplyr::select (
    Group,
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    !"Total_duration_of_fixations.Disruptive_Person",
    !"Number_of_fixations.Disruptive_Person",
    !"Average_duration_of_fixations.Disruptive_Person"
  ) %>%
  rowwise() %>%
  transmute(
    Group = Group,
    Participant = Participant,
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
  ) %>%
  mutate(
    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
    Group = as_factor(Group)
  ) %>%
  drop_na() -> df_aoi_sum

# N, M, SD, min & max number of fixation (micro-teaching unit)
nof.table <-
  df_aoi_sum %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Sum_number_fixation), digits = 2),
    "SD" = round(sd(Sum_number_fixation), digits = 2),
    "Min" = round(min(Sum_number_fixation), digits = 2),
    "Max" = round(max(Sum_number_fixation), digits = 2)
  )

knitr::kable(nof.table,
             caption = "N, M, SD, min & max number of fixations (micro-teaching unit)")

# plotting number of fixations (micro-teaching unit)
df_aoi_sum %>%
  ggplot(mapping = aes(x = Group, y = Sum_number_fixation)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 2500) +
  labs(x = "", y = "Number of fixations") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixation\n(micro-teaching unit)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_group

@@

# NUMBER OF FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(
  x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
  y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
  var.equal = TRUE
)

# NUMBER OF FIXATIONS on all AOIs
# effect size for expertise differences
d_number_all <- CohenD(
  x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
  y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
  na.rm = TRUE
)

@@

# filter group & total duration & number fixation (AOI students)
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = Group,
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
  ) %>%
  mutate(
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
    Group = as_factor(Group)
  ) -> df_aoi_stud

# N, M, SD, min & max number of fixations (AOI students)
nof.stud.table <-
  df_aoi_stud %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Stud_number_fixation), digits = 2),
    "SD" = round(sd(Stud_number_fixation), digits = 2),
    "Min" = round(min(Stud_number_fixation), digits = 2),
    "Max" = round(max(Stud_number_fixation), digits = 2)
  )

knitr::kable(nof.stud.table,
             caption = "N, M, SD, min & max number of fixations (AOI students)")

# plotting average duration on AOI Students
df_aoi_stud %>%
  ggplot(mapping = aes(x = Group, y = Stud_number_fixation)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  labs(x = "", y = "Number of fixations") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations\n(AOI students)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_stud

@@

# NUMBER OF FIXATIONS on AOI students 
# t-test for expertise differences
t.test(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
       var.equal = TRUE)

# NUMBER OF FIXATIONS on AOI students
# effect size for expertise differences
d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
                      y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
                      na.rm = TRUE)

@@

# filter group, participants, total duration & number fixation in entire micro-teaching unit
df_aoi_sum %>%
  group_by(Group) %>% 
  mutate(
    GRI = round(Average_duration_mtu / Sum_number_fixation, digits = 2),
    )-> df_gri

@@

# demo data 
df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  filter(!LI06_05 == 201,
         !LI06_05 == 223,
         !LI06_05 == 232) %>% # exclude participant due to missing eye tracking data
  transmute(Participant = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            )

@@

# rating scales
df_sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201,
               223,
               232),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>% 
  rename(Participant = ID) %>%
  group_by(Participant) %>% 
  summarise(
    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
    )%>% 
  dplyr::select(Participant,
                Mean_disrupption_appraisal,
                Mean_confidence_appraisal,
                Mean_prevalence_rating)

# sjt
df_sjt <-
  read_excel("./data/SJT.xlsx") %>%
  dplyr::select(UI06_05, # Participant
                SJT_AL_gek, # Monitoring
                SJT_ST_gek, # Managing momentum
                SJT_R_gek, # Rules and routines
                SJT_KF_gek) %>% # All
  filter(!UI06_05 %in% c(201, 223, 232)) %>%  # exclude ID with no eye tracking data
  transmute(
    Participant = UI06_05,
    SJT_Monitoring = round(SJT_AL_gek, 2),
    SJT_Managing_momentum = round(SJT_ST_gek, 2),
    SJT_Rules_routines = round(SJT_R_gek, 2),
    SJT_All = round(SJT_KF_gek, 2)
  )

# classroom questionnaire
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
                LP01_01:LP01_08) %>% # non- & paraverbal communication
  filter(!LI06_05 %in% c(201, 223, 232)) %>% # exclude ID with no eye tracking data
  rename(Participant = LI06_05) %>%
  group_by(Participant) %>%
  transmute(
    Participant = Participant,
    "Quest_All" = round(mean(c_across(starts_with(
      "L"
    )), na.rm = TRUE), 2),
    "Quest_classroom_management" = round(mean(c_across(starts_with(
      "LM"
    )), na.rm = TRUE), 2),
    "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
      "LP"
    )), na.rm = TRUE), 2)
  )

@@

# create a correlation matrix
cor_tab <- 
  df_merge %>% 
  cor(method = "spearman") %>% 
  round(., digits = 2)

>>>>

   work_data <-
     read_tsv(file = paste0("data/", i),
              locale = locale(decimal_mark = ",")) %>%
     dplyr::select(Group,
                   Participant,
                   TOI,
                   Duration_of_interval,
                   starts_with("Total_duration_of_fixations"),
                   starts_with("Average_duration_of_fixations"),
                   starts_with("Number_of_fixations"),
                   starts_with("Time_to_first_fixation")
     )

@@

@@

# filter group, participants, total duration & number fixation (micro-teaching unit)
df_aoi %>%
  filter(TOI == "Lesson") %>% 
  dplyr::select (
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    !"Total_duration_of_fixations.Disruptive_Person",
    !"Number_of_fixations.Disruptive_Person",
    !"Average_duration_of_fixations.Disruptive_Person"
  ) %>%
  rowwise() %>%
  transmute(
    Group = Group,
    Participant = Participant,
    Duration_of_interval = Duration_of_interval, 
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
    Number_fixation_msec_mtu = round(Sum_number_fixation / Duration_of_interval, digits = 6),
    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
    Group = as_factor(Group)
  ) %>%
  drop_na() -> df_aoi_sum

# N, M, SD, min & max number of fixation per minute (micro-teaching unit)
nof.table <-
  df_aoi_sum %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Number_fixation_min_mtu), digits = 2),
    "SD" = round(sd(Number_fixation_min_mtu), digits = 2),
    "Min" = round(min(Number_fixation_min_mtu), digits = 2),
    "Max" = round(max(Number_fixation_min_mtu), digits = 2)
  )

knitr::kable(nof.table,
             caption = "N, M, SD, min & max number of fixation per minute (micro-teaching unit)")

# plotting number of fixations (micro-teaching unit)
df_aoi_sum %>%
  ggplot(mapping = aes(x = Group, y = Number_fixation_min_mtu)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 150) +
  labs(x = "", y = "Number of fixations per minute") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations per minute\n(micro-teaching unit)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_group

@@

# NUMBER OF FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(
  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
  var.equal = TRUE
)

# NUMBER OF FIXATIONS on all AOIs
# effect size for expertise differences
d_number_all <- CohenD(
  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
  na.rm = TRUE
)

@@

# filter group & total duration & number fixation (AOI students)
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_sec = round(Duration_of_interval_sec / Stud_number_fixation, digits = 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0)
    ) -> df_aoi_stud

# N, M, SD, min & max number of fixations (AOI students)
nof.stud.table <-
  df_aoi_stud %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Stud_number_fixation_sec), digits = 2),
    "SD" = round(sd(Stud_number_fixation_sec), digits = 2),
    "Min" = round(min(Stud_number_fixation_sec), digits = 2),
    "Max" = round(max(Stud_number_fixation_sec), digits = 2)
  )

knitr::kable(nof.stud.table,
             caption = "N, M, SD, min & max number of fixations per second (AOI students)")

# plotting average duration on AOI Students
df_aoi_stud %>%
  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_sec)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 4) + 
  labs(x = "", y = "Number of fixations per seconds") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations per second\n(AOI students)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_stud

@@

# NUMBER OF FIXATIONS on AOI students 
# t-test for expertise differences
t.test(x = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Expert"],
       y = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Novice"],
       var.equal = TRUE)

# NUMBER OF FIXATIONS on AOI students
# effect size for expertise differences
d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Expert"],
                      y = df_aoi_stud$Stud_number_fixation_sec[df_aoi_stud$Group == "Novice"],
                      na.rm = TRUE)

@@

# filter group, participants, total duration & number fixation in entire micro-teaching unit
df_aoi_sum %>%
  group_by(Group) %>% 
  mutate(
    GRI = round(Average_duration_mtu / Number_fixation_msec_mtu, digits = 2),
    )-> df_gri

@@

# demo data 
df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  filter(!LI06_05 == 201,
         !LI06_05 == 223) %>% # exclude participant due to missing eye tracking data
  transmute(Participant = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            )

@@

# rating scales
df_sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201,
               223),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>% 
  rename(Participant = ID) %>%
  group_by(Participant) %>% 
  summarise(
    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
    )%>% 
  dplyr::select(Participant,
                Mean_disrupption_appraisal,
                Mean_confidence_appraisal,
                Mean_prevalence_rating)

# sjt
df_sjt <-
  read_excel("./data/SJT.xlsx") %>%
  dplyr::select(UI06_05, # Participant
                SJT_AL_gek, # Monitoring
                SJT_ST_gek, # Managing momentum
                SJT_R_gek, # Rules and routines
                SJT_KF_gek) %>% # All
  filter(!UI06_05 %in% c(201, 223)) %>%  # exclude ID with no eye tracking data
  transmute(
    Participant = UI06_05,
    SJT_Monitoring = round(SJT_AL_gek, 2),
    SJT_Managing_momentum = round(SJT_ST_gek, 2),
    SJT_Rules_routines = round(SJT_R_gek, 2),
    SJT_All = round(SJT_KF_gek, 2)
  )

# classroom questionnaire
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
                LP01_01:LP01_08) %>% # non- & paraverbal communication
  filter(!LI06_05 %in% c(201, 223)) %>% # exclude ID with no eye tracking data
  rename(Participant = LI06_05) %>%
  group_by(Participant) %>%
  transmute(
    Participant = Participant,
    "Quest_All" = round(mean(c_across(starts_with(
      "L"
    )), na.rm = TRUE), 2),
    "Quest_classroom_management" = round(mean(c_across(starts_with(
      "LM"
    )), na.rm = TRUE), 2),
    "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
      "LP"
    )), na.rm = TRUE), 2)
  )

@@

# create a correlation matrix
cor_tab <- 
  df_merge %>% 
  cor(method = "pearson") %>% 
  round(., digits = 2)
